The fifteen-dimensional chemical-abundance gradient \\ in the Milky Way disk

### 2016-02-21 papers/gradients/gradients.tex
moving furniture in prep for ref response

\title{The fifteen-dimensional chemical-abundance gradient in the Milky Way disk}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Melissa~Ness\altaffilmark{4},
        Andrew~R.~Casey\altaffilmark{5},
        Hans-Walter~Rix\altaffilmark{4}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics,
  New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}
\email{david.hogg@nyu.edu}

@@

\keywords{
  Galaxy: abundances
  ---
  Galaxy: stellar content
  ---
  stars: abundances
  ---
  stars: formation
  ---
  stars: kinematics and dynamics
  ---
  Galaxy: kinematics and dynamics
}

@@

@@

\acknowledgements
It is a pleasure to thank
  Anna~Y.~Q.~Ho (Caltech),
  Jeremy~Magland (\acronym{SCDA}), and
  the Blanton--Hogg group meeting
for valuable comments and discussions.
This project was funded in part by
  the \acronym{NSF} (grants \acronym{IIS-1124794}, \acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  the Moore-Sloan Data Science Environment at \acronym{NYU}, and
  the European Research Council under the
  European Union's Seventh Framework Programme (FP~7)
  \acronym{ERC} Grant Agreement n.~\acronym{[320360, 321035]}).
This research made use of the \acronym{NASA} \project{Astrophysics Data System}.

>>>>

\title{The fifteen-dimensional chemical-abundance gradient \\ in the Milky Way disk}
\author{David~W.~Hogg\altaffilmark{1,2,3,4},
        Melissa~Ness\altaffilmark{4},
        Andrew~R.~Casey\altaffilmark{5},
        Hans-Walter~Rix\altaffilmark{4}}
\altaffiltext{1}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics,
  New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{5}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3~0HA, UK}

@@

\keywords{
  Galaxy: abundances
  ---
  Galaxy: disk
  ---
  Galaxy: kinematics and dynamics
  ---
  Galaxy: stellar content
  ---
  stars: abundances
  ---
  stars: formation
  ---
  stars: kinematics and dynamics
}

@@

\section{Data}

\apogee.

\thecannon\ and abundances.

distances.

\section{Analyses and results}

@@

\section{Discussion}

whatever.

\acknowledgements
It is a pleasure to thank
  Dan~Foreman-Mackey (UW),
  Anna~Y.~Q.~Ho (Caltech),
  and the Blanton--Hogg group meeting
for valuable comments and discussions.
This project was funded in part by
  the \acronym{NSF} (grants \acronym{IIS-1124794}, \acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  the Moore-Sloan Data Science Environment at \acronym{NYU}, and
  the European Research Council under the
  European Union's Seventh Framework Programme (FP~7)
  \acronym{ERC} Grant Agreement nos.~\acronym{[320360, 321035]}.
This research made use of the \acronym{NASA} \project{Astrophysics Data System}.
